Figures for conference paper

### 2019-06-05 Conference/COPA2019/paper/conference figures COPA2019.Rmd
relocate scripts for conference configures in conference folder

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())

@@

output_folder <- "Conference/COPA2019/paper/figures"
plot_width <- 6
plot_height <- plot_width / 1.6 
```

@@

## Table
```{r}
conformal_results %>%
  filter(significance %in% c(0.05, 0.1, 0.2)) %>%
  group_by(course, significance) %>%
  summarize(width_med  = median(width),
            error_rate = mean(!hit)) %>%

>>>>

# TODO: set working directory to project directory
setwd("C:/Users/JeanLuc/Desktop/Job/DARS/DARS")

knitr::opts_chunk$set(echo = FALSE)
theme_set(theme_light())
knitr::opts_chunk$set(fig.path = "figures/")

@@

output_folder <- "figures"
plot_width <- 4
plot_height <- plot_width / 1.6 
```

@@

## Table
```{r}
conformal_results %>%
  filter(significance < 0.2) %>%
  group_by(course, significance) %>%
  summarize(width_med  = median(width),
            error_rate = mean(!hit)) %>%
